---
title: "2018-12-21_Hampstead_24"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    theme: cerulean
    highlight: pygments
---


# Load Requirements

## Load Useful Libraries 

```{r}
library(dplyr)
library(stringr)
```

## Load Useful Variables

```{r}
source("~/Desktop/config.R")
source("~/Desktop/helpers.R")

# switch to access API (TRUE) or not (FALSE)
get_api_data <- TRUE
```


# Get Data

## Get MRI Scan Data from UM Box

### Download spreadsheet as df
```{r}
file_id <- 320718450581

boxr::box_auth(client_id = BOX_CLIENT_ID, client_secret = BOX_CLIENT_SECRET)
# boxr::box_dl(file_id = 320718450581, overwrite = TRUE)
df_mri <- boxr::box_read_excel(file_id = file_id)
names(df_mri)
df_mri <- df_mri %>% 
  dplyr::filter(!is.na(UDS_ID)) %>% 
  dplyr::mutate(UDS_ID = as.integer(UDS_ID)) %>% 
  dplyr::mutate(Scan_Date = as.Date(Scan_Date))

df_mri <- df_mri %>% 
  dplyr::mutate(ptid = dplyr::case_when(
    nchar(UDS_ID) == 3 ~ paste0('UM00000', UDS_ID),
    nchar(UDS_ID) == 4 ~ paste0('UM0000', UDS_ID),
    TRUE ~ NA_character_
  )) %>% 
  dplyr::select(ptid, dplyr::everything()) %>% 
  dplyr::arrange(ptid, dplyr::desc(Scan_Date))
```

### Get UMMAP IDs of MRI scans

```{r}
mri_ids <- df_mri %>% distinct(ptid) %>% pull()

umid_records <- mri_ids %>% paste(collapse = ",")
```


## Define UDS/MiNDSet Data Fields/Forms

### UDS 2
```{r}
fields_u2_raw <- c("subject_id"
                   , "a1form_date"
                   , "dob"
                   , "race"
                   , "sex"
                   , "handed"
                   , "educ"
                   , "maristat")

forms_u2_raw <- c("form_b5_behavioral_assessment_npi_q"
                  , "form_c1_mmse_and_npsych")

fields_u2 <- fields_u2_raw %>% paste(collapse = ",")
forms_u2 <- forms_u2_raw %>% paste(collapse = ",")
```

### UDS 3
```{r}
fields_u3_raw <- c("ptid"
                   , "form_date"
                   , "dob"
                   , "race"
                   , "sex"
                   , "handed"
                   , "educ"
                   , "maristat"
                   , "fu_sex"
                   , "fu_maristat")

forms_u3_raw <- c("ivp_b5"
                  , "ivp_c2"
                  , "fvp_b5"
                  , "fvp_c2"
                  , "oltt"
                  , "hol_questionnaire"
                  , "ipad_tool_box")

fields_u3 <- fields_u3_raw %>% paste(collapse = ",")
forms_u3 <- forms_u3_raw %>% paste(collapse = ",")
```

### MiNDSet Registry
```{r}
fields_ms_raw <- c("subject_id"
                   , "exam_date"
                   , "uds_dx")

fields_ms <- fields_ms_raw %>% paste(collapse = ",")
```


## Retrieve Data via REDCap API

### UDS 2
```{r}
if (get_api_data) {
  json_u2 <- rc_api_get(token   = REDCAP_API_TOKEN_UDS2,
                        fields  = fields_u2,
                        forms   = forms_u2,
                        records = umid_records)
}

df_u2 <- jsonlite::fromJSON(json_u2) %>% na_if("")
```

### UDS 3
```{r}
if (get_api_data) {
  json_u3 <- rc_api_get(token   = REDCAP_API_TOKEN_UDS3n,
                        fields  = fields_u3,
                        forms   = forms_u3,
                        records = umid_records)
}

df_u3 <- jsonlite::fromJSON(json_u3) %>% na_if("")
```

### MiNDSet Registry
```{r}
if (get_api_data) {
  json_ms <- rc_api_get(token   = REDCAP_API_TOKEN_MINDSET,
                        fields  = fields_ms,
                        records = umid_records,
                        raw     = FALSE)
}

df_ms <- jsonlite::fromJSON(json_ms) %>% na_if("")
```


## Write Raw Data to CSV

### UDS 2
```{r}
readr::write_csv(df_u2, "df_u2.csv", na = "")
```

### UDS 3
```{r}
readr::write_csv(df_u3, "df_u3.csv", na = "")
```

### MiNDSet Registry
```{r}
readr::write_csv(df_ms, "df_ms.csv", na = "")
```


# Process Data

## Clean Data

### UDS 2
```{r}
# Clean out records with missing dates or "x.5" visits,
#   and deselect some redundant fields
df_u2_cln <- df_u2 %>% 
  mutate(dob = lubridate::mdy(dob),
         a1form_date = lubridate::ymd(a1form_date)) %>% 
  filter(!is.na(a1form_date)) %>% 
  filter(str_detect(redcap_event_name, "^visit_\\d{1,2}")) %>% 
  select(-b5ptid, -b5_formdate, -b5_visit_month, -b5_visit_day, -b5_visit_yr,
         -c1ptid, -c1form_date, -c1_visit_month, -c1_visit_day, -c1_visit_yr)

# rename key fields
df_u2_cln_rn <- df_u2_cln %>% 
  rename(ptid = subject_id,
         form_date = a1form_date)
```

### UDS 3
```{r}
# Clean out records with missing dates or "x.5" visits
df_u3_cln <- df_u3 %>% 
  mutate(dob = lubridate::ymd(dob),
         form_date = lubridate::ymd(form_date)) %>% 
  filter(!is.na(form_date)) %>% 
  filter(str_detect(redcap_event_name, "^visit_[1-9]"))

# Rename some fields
names(df_u3_cln) <- str_replace_all(string = names(df_u3_cln),
                                    pattern = "_c2",
                                    replacement = "")

# Collapse IFT fields
df_u3_cln_clps <- df_u3_cln
collapsible_fields_u3 <- get_ift_dups(names(df_u3_cln))
for (field in collapsible_fields_u3) {
  df_u3_cln_clps <- collapse_ift_cols(df_u3_cln_clps, !!field) # <= NOTICE !!
}
```

### MiNDSet Registry
```{r}
# Clean out records with missing dates or "x.5" visits
df_ms_cln <- df_ms %>% 
  filter(!is.na(exam_date)) %>% 
  select(-redcap_event_name) %>% 
  mutate(exam_date = lubridate::ymd(exam_date))
```


## Join Data

### UDS 2 + UDS 3
```{r}
names_u2 <- names(df_u2_cln_rn)
names_u3 <- names(df_u3_cln_clps)
length(unique(c(names_u2, names_u3)))
df_u2_u3 <- bind_rows(df_u2_cln_rn, df_u3_cln_clps)
ncol(df_u2_u3)
```

### UDS 2/3 + MiNDSet Registry

```{r}
df_u2_u3_ms <-
  FuzzyDateJoin::outer_left(
    df_u2_u3, df_ms_cln,
    x_id_col = "ptid", y_id_col = "subject_id",
    x_date_col = "form_date", y_date_col = "exam_date",
    x_intvl_less = 120, x_intvl_more = 120,
    keep_y_id = FALSE
  )
```


### Fill missing DOB values
```{r}
df_u2_u3_ms <- df_u2_u3_ms %>% 
  arrange(ptid, desc(form_date))

for (i in 2:nrow(df_u2_u3_ms)) {
  # cat(paste(i, "\n"))
  
  prev_id <- df_u2_u3_ms[[i-1, "ptid"]]
  curr_id <- df_u2_u3_ms[[i, "ptid"]]
  prev_dob <- df_u2_u3_ms[[i-1, "dob"]]
  curr_dob <- df_u2_u3_ms[[i, "dob"]]
  
  if (prev_id == curr_id && !is.na(prev_dob) && is.na(curr_dob)) {
    df_u2_u3_ms[[i, "dob"]] <- prev_dob
  }
}

df_u2_u3_ms <- df_u2_u3_ms %>% 
  arrange(ptid, form_date)

for (i in 2:nrow(df_u2_u3_ms)) {
  # cat(paste(i, "\n"))
  
  prev_id <- df_u2_u3_ms[[i-1, "ptid"]]
  curr_id <- df_u2_u3_ms[[i, "ptid"]]
  prev_dob <- df_u2_u3_ms[[i-1, "dob"]]
  curr_dob <- df_u2_u3_ms[[i, "dob"]]
  
  if (prev_id == curr_id && !is.na(prev_dob) && is.na(curr_dob)) {
    df_u2_u3_ms[[i, "dob"]] <- prev_dob
  }
}
```

### Calculate age
```{r}
df_u2_u3_ms <- calculate_age(df_u2_u3_ms, dob, form_date)
```

### Reorder columns
```{r}
df_u2_u3_ms <- df_u2_u3_ms %>% 
  select(-redcap_event_name, -dob) %>% 
  select(ptid, form_date, uds_dx, age, age_exact, everything())
```


# Write Data

## Write to CSV

```{r}
readr::write_csv(df_u2_u3_ms, "df_u2_u3_ms.csv", na = "")
```


























